\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-05-03 paper_final.tex
Finished liar proof

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{bbm}
\usepackage{parskip}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}

@@

\newcommand{\learn}{\mathcal{A}_{w_0}^\eta}

@@

Therefore 
$T_\epsilon \leq  2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$

>>>>

\usepackage{amsfonts}       % blackboard math symbols
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}
\usepackage{bbm}

@@

\newcommand{\learn}{\mathcal{A}_{w_0}^\eta}
\newcommand{\radian}{\text{radian}}

@@

Therefore 
$\mathbb{T}_\epsilon \leq  2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$

\section{Teaching Dimension for unknown $\eta$ and $w_0$}
Here we show a strategy where we know neither the learning rate or the initial weight vector of our perceptron learner. With prior knowledge of some reasonable bound on the magnitude of $w_0$ and $\eta$, we show a strategy that gives an upper bound on the approximate teaching dimension in this scenario.

\subsection{Ability to Lie}
Allowing the teacher to lie, or give $(x,y)$ that disagree with $w^*$, make teaching the learner very easy. In fact in this scenario, the approximate teaching dimension is $2$.
\\
\\
\\
\textbf{Theorem 5.} \textit{
Let $w_0$, $\eta$ be unknown with $\lVert w_0 \rVert \leq b$ and $0 < \eta_{\min} \leq \eta$.
Then with the ability to lie, $\mathbb{T}_{\epsilon}(w^*, \learn) = 2$
}
\\
\\
\\
\textit{Proof.}
WLOG assume $\lVert w^* \rVert = 1$
Select an $x_1 = \frac{b(2-\epsilon)}{\eta_{\min} \epsilon}w^*, \qquad y_1 = -1$
Then give $(x_1 , y _1)$ to the perceptron.
Then let $x_2 = 2x_1, \qquad y_2 = 1$ and give $(x_2, y_2)$ to the perceptron.

Then there are two cases.

\textbf{Case 1:} The perceptron incorrectly predicts $y = 1$ for $x_1$.

Then 
$
w_1 = w_0 - \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}w^*
$

Then 
$$y_2 \langle w_1, 2x_1 \rangle
$$
$$
 = \langle w_0, 2x_1 \rangle - 2\frac{(\eta b(2-\epsilon))^2}{(\eta_{\min}\epsilon)^2}
 \leq 2b\frac{\eta b(2-\epsilon)}{\eta_{\min}\epsilon}
-  2\frac{(\eta b(2-\epsilon))^2}{(\eta_{\min}\epsilon)^2} 
$$
$$
\leq 2\frac{\eta b^2(2-\epsilon)}{\eta_{\min}\epsilon}
-  2\frac{\eta (b(2-\epsilon))^2}{\eta_{\min}\epsilon^2}
< 0 \qquad \text{ for } \epsilon < 0
$$
Therefore $(x_2, y_2)$ causes and update and
$w_2 =  w_0 + \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}w^* $

Then
$$
\frac{\langle w_2 , w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} = \frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} + \langle w_0, w^* \rangle}{\lVert w_2 \rVert} \geq \frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} - b}{b + \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}}
$$
Which implies
$$
1 - \frac{\langle w_2 , w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} \leq \frac{2b}{b + \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}}
\leq
\frac{2}{1 + \frac{2-\epsilon}{\epsilon}} = \epsilon
$$

\textbf{Case 2:} $(x_1, y_1)$ does not cause an update.

Then clearly $(x_2, y_2)$ will cause an update and
$$
w_2 = w_0 + 2\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}w^* 
$$
so,
$$
\frac{\langle w_2 , w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} = 2\frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} + \langle w_0, w^* \rangle}{\lVert w_2 \rVert} \geq \frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} + \langle w_0, w^* \rangle}{\lVert w_2 \rVert} \geq 1 - \epsilon
$$

We have thus shown that we can get an $\epsilon$ approximate bound with only 2 examples. It should be clear that this is impossible to do with $1$ example since without knowledge of $w_0$ there exists no $(x_1, y_1)$ that can guarantee the perceptron will update.

So 
$
\mathbb{T}_{\epsilon}(w^*, \learn) = 2
$

\textbf{Corrolary}
\textit{
Theorem 5 also shows that with known $\eta$ and ability to lie the approximate teaching dimension is still 2. This is 1 less the the $\epsilon$ approximate Teaching dimension where we cannot lie. \cite{perceptron}
}
